### 2019-09-29 paper-two/paper-two.tex
mostly done anatomy of paper 2

@@

The SN is an intrinsically connected large-scale network anchored in the Anterior Insula (AI) and dorsal Anterior Cingulate Cortex. Both these regions have reached a high degree of specialization in the great apes. It is the collection of the regions in the brain that help decide which stimuli deserves our attention. It acts as a switch between the internally directed DMN and the externally directed Central Executive Network (involved in high level cognitive functions) (7).

The Salience Network consists of the Anterior Cingulate Cortex and the Insula. It helps to switch between the Default Mode Network and the Central Executive Network
a) Anterior Cingulate Cortex (ACC): The ACC is the front end of the cingulate cortex and collars around the corpus callosum (the band connecting the two hemispheres of the brain). It is the connector between the emotional (limbic system) and the cognitive part of the brain. It is involved in functions such as attention allocation, reward anticipation, decision making, morality, impulse control, emotional awareness and registering pain (8–12). It also appears to play a role in the regulation of Autonomic functions such as blood pressure and heart rate (13).
b) Anterior Insular Cortex (AIC): The insula is a part of the cerebral cortex that is located deep within the sulcus (which is the fissure separating the four lobes of the brain). The AIC projects itself into the amygdala. It is involved in multimodal sensory processing such as audio-visual integration tasks, interoceptive awareness (so its activity is directly related to ones sense of internal body states), empathy and conscious awareness (14). It also plays a role in the regulation of autonomic functions such as bodily sensations (as well as where the degree of pain is judged), taste and control of the immune system (15).
The AIC and ACC together give rise to our interoceptive and conscious self-awareness.
Central Executive Network:
This network is activated when a high-level cognitive tasks or external goal-oriented tasks are being performed. Executive functions are cognitive processes involved in cognitive control of behavior.
The regions of the brain involved in this are Dorsolateral Prefrontal Cortex, Orbito Frontal Cortex and the Posterior Parietal Cortex.
Dorsolateral Prefrontal Cortex (DL-PFC): It is a part of the pre-frontal cortex and is found in primates and humans. It is a part of the Central Executive Network. The DL-PFC is involved in higher cognitive processes including working memory (holding different pieces of information and manipulating and using them for tasks), selective attention, cognitive flexibility (switching between tasks) and planning. It also seems to be involved in social cognition and lying and increases dopamine levels in the brain.
Barbey AK, Koenigs M, Grafman J (May 2013). “Dorsolateral prefrontal contributions to human working memory” (PDF). Cortex. 49 (5): 1195–1205.
Monsell S (2003). “Task switching”. Trends in Cognitive Sciences. 7 (3): 134–140. doi:10.1016/S1364–6613(03)00028–7. PMID 12639695.
Ito, Ayahito; Abe, Nobuhito; Fujii, Toshikatsu; Hayashi, Akiko; Ueno, Aya; Mugikura, Shunji; Takahashi, Shoki; Mori, Etsuro (2012). “The contribution of the dorsolateral prefrontal cortex to the preparation for deception and truth-telling”. Brain Research. 1464: 43–52. doi:10.1016/j.brainres.2012.05.004
Orbito Frontal Cortex (OFC): This is an area found in front of both the hemispheres and just above the eye. It is a part of the Pre-Frontal Cortex and it is thought to be involved in the cognitive process of decision making. It is thought to represent emotion and reward in decision making. It also receives input from multiple sensory modalities and in turn activates the amygdala and the hypothalamus
Fuster, J.M. The Prefrontal Cortex, (Raven Press, New York, 1997
Rolls, ET (November 2004). “Convergence of sensory systems in the orbitofrontal cortex in primates and brain design for emotion”. The Anatomical Record Part A: Discoveries in Molecular, Cellular, and Evolutionary Biology. 281 (1): 1212–25. doi:10.1002/ar.a.20126
Price, Joseph L. (2006). “Chapter 3: Connections of the orbital cortex”. In Rauch, Scott L.; Zald, David H. (eds.). The Orbitofrontal Cortex. New York: Oxford University Press. p. 45.
Posterior Parietal Cortex (PPC): It receives information from the Auditory, Visual and Somatosensory systems and in turn activates the motor cortex or DL-PFC.
Martin, R. E. (n.d.). Let’s Get to Know the Parietal Lobes! [PDF]. Retrieved from \url{http://gablab.mit.edu/downloads/Parietal_Primer.pd}

Approximate location of the OFC on an MRI
(Maybe remove)
The limbic system: The limbic system is a complex set of structures that lies on both sides of the thalamus, just under the cerebrum. It includes the hypothalamus, the hippocampus, the amygdala, and several other nearby areas. It appears to be primarily responsible for our emotional life, and has a lot to do with the formation of memories.

The course

@@

Pardo JV, Pardo PJ, Janer KW, Raichle ME (January 1990). “The anterior cingulate cortex mediates processing selection in the Stroop attentional conflict paradigm”. Proceedings of the National Academy of Sciences of the United States of America. 87 (1): 256–9. doi:10.1073/pnas.87.1.256. PMID 2296583.
Bush G, Vogt BA, Holmes J, Dale AM, Greve D, Jenike MA, Rosen BR (January 2002). “Dorsal anterior cingulate cortex: a role in reward-based decision making”. Proceedings of the National Academy of Sciences of the United States of America. 99 (1): 523–8. doi:10.1073/pnas.012470999. PMC 117593. PMID 11756669.
Sevinc G, Gurvit H, Spreng RN (July 2017). “Salience network engagement with the detection of morally laden information”. Social Cognitive and Affective Neuroscience. 12 (7): 1118–1127. doi:10.1093/scan/nsx035. PMID 28338944.
Jackson PL, Brunet E, Meltzoff AN, Decety J (2006). “Empathy examined through the neural mechanisms involved in imagining how I feel versus how you feel pain”. Neuropsychologia. 44 (5): 752–61. doi:10.1016/j.neuropsychologia.2005.07.015. PMID 16140345.
Bush G, Luu P, Posner MI (June 2000). “Cognitive and emotional influences in anterior cingulate cortex”. Trends in Cognitive Sciences. 4 (6): 215–222. doi:10.1016/S1364–6613(00)01483–2. PMID 10827444
Gianaros PJ, Derbyshire SW, May JC, Siegle GJ, Gamalo MA, Jennings JR. Anterior cingulate activity correlates with blood pressure during stress. Psychophysiology. 2005;42(6):627–35.
Xiaosi Gu, Patrick R. Hof, Karl J. Friston, Jin Fan. J Comp Neurol. 2013 Oct 15; 521(15): 3371–3388.
Rolls ET. Functions of the anterior insula in taste, autonomic, and related functions. Brain Cogn. 2016 Dec;110:4–19.
Lazar SW; Bush George; Gollub RL.; Fricchione, GL.; Khalsa G; Benson H. Functional brain mapping of the relaxation response and meditation.
Neuroreport. 11(7):1581–1585, May 15, 2000.
J. Muñoz-Ortiz, E. Muñoz-Ortiz, L. López-Meraz, L. Beltran-Parrazal, C. Morgado-Valle. The pre-Bötzinger complex: Generation and modulation of respiratory rhythm, Neurología (English Edition), 2018, ISSN 2173–5808,
https://doi.org/10.1016/j.nrleng.2018.05.006.
REMPEL‐CLOWER, N. L. (2007), Role of Orbitofrontal Cortex Connections in
Emotion. Annals of the New York Academy of Sciences, 1121:
72–86. doi:10.1196/annals.1401.026

@@

>>>>

\subsection{Central Executive Network}

The CEN is activated when high-level cognitive tasks or external goal-oriented tasks
are being performed. Executive functions are cognitive processes involved in
cognitive control of behavior. The regions of the brain involved in executive
functions are Dorsolateral Prefrontal Cortex (DL-PFC), Orbito Frontal Cortex (OFC),
and the Posterior Parietal Cortex (PPC).

\subsubsection{Dorsolateral Prefrontal Cortex}

The DL-PFC is a part of the Prefrontal Cortex found in primates, including
humans. The DL-PFC is involved in higher cognitive processes including working memory
(holding different pieces of information, manipulating them, and using them for
tasks), selective attention, cognitive flexibility (switching between tasks) and
planning. It also seems to be involved in social cognition and lying. The DL-PFC can
increase dopamine levels in the brain. \cite{dlpfcmemory,dlpfctasks,dlpfclying}

\subsubsection{Orbito Frontal Cortex}

The OFC is an area found in front of both hemispheres of the brain, just above the
eye. It is again part of the Prefrontal Cortex and is thought to be involved in
decision making through emotion and reward. It also receives input from multiple
sensory modalities and in turn activates the Amygdala and the
Hypothalamus. \cite{theprefrontalcortex,ofcprimates,theorbitofrontalcortex}

\subsubsection{Posterior Parietal Cortex}

The PPC receives information from the auditory, visual and somatosensory systems and
in turn activates the Motor Cortex or DL-PFC. \cite{parietallobes}

[ TODO: why? how? expand. ]

[ TODO: image of Approximate location of the OFC on an MRI ]

@@

The SN is an intrinsically connected large-scale network anchored in the Anterior
Insular Cortex (AIC) and Dorsal Anterior Cingulate Cortex (ACC). Both regions have reached a
high degree of specialization in the great apes. It is the collection of the regions
in the brain that help decide which stimuli deserves our attention. It acts as a
switch between the internally-directed DMN and the externally-directed Central
Executive Network. \cite{saliencenetwork}

\subsubsection{Anterior Cingulate Cortex}

The ACC is the front end of the Cingulate Cortex and collars around the Corpus
Callosum, the band connecting the two hemispheres of the brain. It is the connector
between the emotional (Limbic System) and the cognitive (Prefrontal Cortex) part of
the brain. It is involved in functions such as attention allocation, reward
anticipation, decision making, morality, impulse control, emotional awareness and
registering pain. \cite{accstroop,accreward,snmorality,empathypain,acccognitive} It
also appears to play a role in the regulation of Autonomic functions such as blood
pressure and heart rate. \cite{accbloodpressure}

\subsubsection{Anterior Insular Cortex}

The Insula is a part of the Cerebral Cortex located deep within the Sulcus, the
fissure separating the four lobes of the brain. The AIC physically projects itself
into the Amygdala. It is involved in multimodal sensory processing such as
audio-visual integration tasks, interoceptive awareness (so its activity is directly
related to an individual's sense of internal body states), empathy and conscious
awareness. \cite{aicemotion}

It also plays a role in the regulation of autonomic functions such as bodily
sensations (including judgement of the severity of pain), taste, and control of the
immune system. \cite{aicautonomic}

The AIC and ACC together give rise to our interoceptive and conscious
self-awareness. [ TODO: reference ]

\subsection{The Limbic System}

The limbic system is a complex set of structures that lies on both sides of the
Thalamus, just under the Cerebrum. It includes the Hypothalamus, the Hippocampus, the
Amygdala, and several other nearby areas. It appears to be primarily responsible for
our emotional life, and has a lot to do with the formation of memories. [ TODO:
  reference ]

\section{The Course}

@@

Lazar SW; Bush George; Gollub RL.; Fricchione, GL.; Khalsa G; Benson H. Functional brain mapping of the relaxation response and meditation.
Neuroreport. 11(7):1581–1585, May 15, 2000.
J. Muñoz-Ortiz, E. Muñoz-Ortiz, L. López-Meraz, L. Beltran-Parrazal, C. Morgado-Valle. The pre-Bötzinger complex: Generation and modulation of respiratory rhythm, Neurología (English Edition), 2018, ISSN 2173–5808,
https://doi.org/10.1016/j.nrleng.2018.05.006.
REMPEL‐CLOWER, N. L. (2007), Role of Orbitofrontal Cortex Connections in
Emotion. Annals of the New York Academy of Sciences, 1121:
72–86. doi:10.1196/annals.1401.026

@@

\bibitem{accstroop}
  Pardo JV, Pardo PJ, Janer KW, Raichle ME.
  \textit{The anterior cingulate cortex mediates processing selection in the Stroop
    attentional conflict paradigm.}
  Proceedings of the National Academy of Sciences of the United States of
  America. 87 (1): 256–9. doi:10.1073/pnas.87.1.256. PMID 2296583. January 1990.

\bibitem{accreward}
  Bush G, Vogt BA, Holmes J, Dale AM, Greve D, Jenike MA, Rosen BR.
  \textit{Dorsal anterior cingulate cortex: a role in reward-based decision making.}
  Proceedings of the National Academy of Sciences of the United States of
  America. 99 (1): 523–8. doi:10.1073/pnas.012470999. PMC 117593. PMID
  11756669. January 2002.

\bibitem{snmorality}
  Sevinc G, Gurvit H, Spreng RN.
  \textit{Salience network engagement with the detection of morally laden
    information.}
  Social Cognitive and Affective Neuroscience. 12 (7):
  1118–1127. doi:10.1093/scan/nsx035. PMID 28338944. July 2017.

\bibitem{empathypain}
  Jackson PL, Brunet E, Meltzoff AN, Decety J.
  \textit{Empathy examined through the neural mechanisms involved in imagining how I
    feel versus how you feel pain.}
  Neuropsychologia. 44 (5): 752–61. doi:10.1016/j.neuropsychologia.2005.07.015. PMID
  16140345. 2006.

\bibitem{acccognitive}
  Bush G, Luu P, Posner MI.
  \textit{Cognitive and emotional influences in anterior cingulate cortex.}
  Trends in Cognitive Sciences. 4 (6):
  215–222. doi:10.1016/S1364–6613(00)01483–2. PMID 10827444. June 2000.

\bibitem{accbloodpressure}
  Gianaros PJ, Derbyshire SW, May JC, Siegle GJ, Gamalo MA, Jennings JR.
  \textit{Anterior cingulate activity correlates with blood pressure during
    stress.}
  Psychophysiology. 42(6):627–35. 2005.

\bibitem{aicemotion}
  Xiaosi Gu, Patrick R. Hof, Karl J. Friston, Jin Fan.
  \textit{Anterior Insular Cortex and Emotional Awareness.}
  J Comp Neurol. 521(15): 3371–3388. 2013-08-15.

\bibitem{aicautonomic}
  Rolls ET.
  \textit{Functions of the anterior insula in taste, autonomic, and related
    functions.}
  Brain Cogn. 110:4–19. December 2016.

\bibitem{dlpfcmemory}
  Barbey AK, Koenigs M, Grafman J.
  \textit{Dorsolateral prefrontal contributions to human working memory.}
  Cortex. 49 (5): 1195–1205. May 2013.

\bibitem{dlpfctasks}
  Monsell S.
  \textit{Task switching.}
  Trends in Cognitive Sciences. 7 (3):
  134–140. doi:10.1016/S1364–6613(03)00028–7. PMID 12639695. 2003.

\bibitem{dlpfclying}
  Ito, Ayahito; Abe, Nobuhito; Fujii, Toshikatsu; Hayashi, Akiko; Ueno, Aya;
  Mugikura, Shunji; Takahashi, Shoki; Mori, Etsuro.
  \textit{The contribution of the dorsolateral prefrontal cortex to the preparation
    for deception and truth-telling.}
  Brain Research. 1464: 43–52. doi:10.1016/j.brainres.2012.05.004. 2012.

\bibitem{theprefrontalcortex}
  Fuster, J.M.
  \textit{The Prefrontal Cortex}
  Raven Press, New York, 1997.

\bibitem{ofcprimates}
  Rolls, ET.
  \textit{Convergence of sensory systems in the orbitofrontal
    cortex in primates and brain design for emotion.}
  The Anatomical Record Part A: Discoveries in Molecular, Cellular, and Evolutionary
  Biology. 281 (1):1212–25. doi:10.1002/ar.a.20126. November 2004.

\bibitem{theorbitofrontalcortex}
  Price, Joseph L.
  \textit{Chapter 3: Connections of the orbital cortex.}
  Rauch, Scott L.; Zald, David H.
  The Orbitofrontal Cortex. p. 45.
  Oxford University Press, New York. 2006.

\bibitem{parietallobes}
  Martin, R. E.
  \textit{Let’s Get to Know the Parietal Lobes!}
  \url{http://gablab.mit.edu/downloads/Parietal_Primer.pdf} [ TODO: 404? ]
